\LARGE \bf Explicit Knowledge and the Deliberative Layer: Lessons Learned

### 2013-03-22 paper.tex
Fixed affiliation

\author{Séverin Lemaignan and Rachid Alami\\
CNRS-LAAS, 7 av. du Colonel Roche, F-31077 Toulouse, France\\
Université de Toulouse, UPS, INSA, INP, ISAE, LAAS, F-31077 Toulouse, France\\
{\tt surname.name@laas.fr}
}

>>>>

\author{Séverin Lemaignan and Rachid Alami\\
CNRS, LAAS, 7 avenue du Colonel Roche, F-31400 Toulouse, France\\
Univ de Toulouse, LAAS, F-31400 Toulouse, France\\
{\tt severin.lemaignan@laas.fr}, {\tt rachid.alami@laas.fr}
}
